---
title: "Problem Set Chapter3 4"
author: "Ed Young"
date: "8/16/2019"
output:
  html_document:
    css: styles.css
    highlight: null
    theme: null
    toc: yes
  toc: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(MASS)
```

### (1) 
$V_\mathbb{C}=P_\mathbb{B}^\mathbb{C} V_\mathbb{B}\textrm{.  Find}P_\mathbb{B}^\mathbb{C}\textrm{ for}\\
\mathbb{C}=
     \begin{bmatrix}
     0&1\\
     1&1
     \end{bmatrix}
\mathbb{B}=
     \begin{bmatrix}
     1&1\\
     0&1
\end{bmatrix}\\
\begin{bmatrix}
     1\\0
\end{bmatrix}=
x\begin{bmatrix}0\\1\end{bmatrix}+
y\begin{bmatrix}1\\1\end{bmatrix}\therefore
\begin{bmatrix}x\\y\end{bmatrix}=\begin{bmatrix}-1\\1\end{bmatrix}\\
\begin{bmatrix}
     1\\1
\end{bmatrix}=
x\begin{bmatrix}0\\1\end{bmatrix}+
y\begin{bmatrix}1\\1\end{bmatrix}\therefore
\begin{bmatrix}x\\y\end{bmatrix}=\begin{bmatrix}0\\1\end{bmatrix}\\
P_\mathbb{B}^\mathbb{C}=\begin{bmatrix}-1&0\\1&1\end{bmatrix}_\mathbb{B}^\mathbb{C}$

     

```{r}
B<-matrix(c(1,0,1,1),nrow=2, ncol=2, byrow=FALSE)
C<-matrix(c(0,1,1,1),nrow=2, ncol=2, byrow=FALSE)
C%*%(solve(B))
```
 
 