---
title: Linear Algebra  Algorithms, Applications, and Techniques
##  Third Edition
author:  Richard Bronson, Gabriel B. Costa, John T. Saccoman
##  Elsevier Inc.
##  Problem Sets
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

#  Chapter 1 
## Problem Set 1.2

(1) Determine the orders of the following products if the order of A is $2\times 4$, the order of B is $4\times 2$, the order of C is $4\times 1$, the order of D is $1\times 2$, and the order of E is $4 \times 4$.
(a) AB, (2X4)(4X2)=(2X2)
(b) BA, (4X2)(2X4)=(4X4)
(c) AC, (2X4)(4X1)=(2X1)
(d) CA, (4X1)(2X4) is not defined
(e) CD, (4X1)(1X2)=(4X2)
(f) AE, (2X4)(4X4)=(2X4)
(g) EB, (4X4)(4X2)=(4X2)
(h) EA, (4X4)(2X4 is not defined)
(i) ABC, ((2X4)(4X2))(4X1)=(2X2)(4X1) is not defined
(j) DAE, ((1X2)(2X4))(4X4)= (1X4)(4X4)=(1X4)
(k) EBA, ((4X4)(4X2))(2X4)=(4X2)(2X4)=(4X4)
(l) EECD.(((4X4)(4X4))(4X1))(1X2)=((4X4)(4X1))(1X2)=(4X1)(1X2)=(4X2)

In Problems 2 through 19, find the indicated products for
\[
A=\begin{bmatrix}
1 & 2 \\
3 & 4
\end{bmatrix}
\]
\[
B=\begin{bmatrix}
5 & 6 \\
7 & 8
\end{bmatrix}
\]
\[
C=\begin{bmatrix}
-1& \quad 0& 1\\
\quad 3& -2& 1
\end{bmatrix}
\]
\[
D=\begin{bmatrix}
\quad 1& \quad 1\\
-1& \quad 3\\
\quad 2& -2
\end{bmatrix}
\]
\[
E=\begin{bmatrix}
-2& \quad 2& \quad 1\\
\quad 0& -2& -1\\
\quad 1& \quad 0& \quad 1\\
\end{bmatrix}
\]
\[
F=\begin{bmatrix}
\quad 0& \quad 1& 2\\
-1& -1& 0\\
\quad 1& \quad 2& 3\\
\end{bmatrix}
\]
\[
x=\begin{bmatrix}
1& -2
\end{bmatrix}
\]
\[
y=\begin{bmatrix}
1 &2 &1
\end{bmatrix}
\]
(2) AB. (3) BA. (4) AC. (5) BC. (6) CB. (7) xA.
(8) xB. (9) xC. (10) Ax. (11) CD. (12) DC. (13) yD.
(14) yC. (15) Dx. (16) xD. (17) EF. (18) FE. (19) yF.

```{r}
A<-matrix(c(1,3,2,4), nrow=2, ncol=2, byrow=FALSE)
B<-matrix(c(5,7,6,8), nrow=2, ncol=2, byrow=FALSE)
C<-matrix(c(-1, 0, 1, 3, -2, 1), nrow=2, ncol=3, byrow=TRUE)
D<-matrix(c(1, 1, -1, 3, 2, -2), nrow=3, ncol=2, byrow=TRUE)
E<-matrix(c(-2, 2, 1, 0, -2, -1, 1, 0, 1), nrow=3, ncol=3, byrow=TRUE)
F<-matrix(c(0, 1, 2, -1, -1, 0, 1, 2, 3), nrow=3, ncol=3, byrow=TRUE)
x<-matrix(c(1, -2), nrow=1, ncol=2, byrow=TRUE)
y<-matrix(c(1,2,1), nrow=1, ncol=3, byrow=TRUE)

writeLines("(2) AB:\t");A %*% B; writeLines("\n")
writeLines("(3) BA:\t");B %*% A; writeLines("\n")
writeLines("(4) AC:\t");A %*% C; writeLines("\n")
writeLines("(5) BC:\t");B %*% C; writeLines("\n")
writeLines("(6) CB:\t Non Conformable");writeLines("\n") 
writeLines("(7) xA:\t");x %*% A; writeLines("\n")
writeLines("(8) xB:\t");x %*% B; writeLines("\n") 
writeLines("(9) xC:\t");x %*% C; writeLines("\n") 
writeLines("(10) Ax:\t Non Conformable"); writeLines("\n") 
writeLines("(11) CD:\t");C %*% D; writeLines("\n") 
writeLines("(12) DC:\t");D %*% C; writeLines("\n") 
writeLines("(13) yD:\t");y %*% D; writeLines("\n")
writeLines("(14) yC:\t Non Conformable"); writeLines("\n") 
writeLines("(15) Dx:\t Non Conformable"); writeLines("\n") 
writeLines("(16) xD:\t Non Conformable"); writeLines("\n") 
writeLines("(17) EF:\t");E %*% F; writeLines("\n") 
writeLines("(18) FE:\t");F %*% E; writeLines("\n") 
writeLines("(19) yF:\t");y %*% F; writeLines("\n")
```
(20) Find AB for 
\[
A=\begin{bmatrix}
2& 6\\
3& 9
\end{bmatrix}
\]
\[
B=\begin{bmatrix}
\quad 3& -6\\
-1& \quad 2
\end{bmatrix}
\]

```{r}
A<-matrix(c(2,3,6,9), nrow=2, ncol=2, byrow=FALSE)
B<-matrix(c(3,-1,-6,2), nrow=2, ncol=2, byrow=FALSE)
writeLines("AB:");A;B;A %*% B
```

(21) Find AB for 
\[
A=\begin{bmatrix}
4& 2\\
2& 1
\end{bmatrix}
\]
\[
B=\begin{bmatrix}
\quad 3& -4\\
-6& \quad 8
\end{bmatrix}
\]

```{r}
A<-matrix(c(4,2,2,1), nrow=2, ncol=2, byrow=FALSE)
B<-matrix(c(3,-4,-6,8), nrow=2, ncol=2, byrow=FALSE)
writeLines("AB:");A;B;A %*% B
```

Find AB and AC for 
\[
A=\begin{bmatrix}
4& 2\\
2& 1
\end{bmatrix}
\]
\[
B=\begin{bmatrix}
1& 1\\
2& 1
\end{bmatrix}
\]
\[
C=\begin{bmatrix}
2& \quad 2\\
0& -1
\end{bmatrix}
\]

```{r}
A<-matrix(c(4,2,2,1), nrow=2, ncol=2, byrow=FALSE)
B<-matrix(c(1,1,2,1), nrow=2, ncol=2, byrow=TRUE)
C<-matrix(c(2,2,0,-1), nrow=2, ncol=2, byrow=TRUE)
writeLines("AB:");A;B;A %*% B; writeLines("\n")
writeLines("AC:");A;C;A %*% C; writeLines("\n")
```

(51) The price schedule for a Chicago to Los Angeles flight is given by
\[
p=\begin{bmatrix}
200 & 350 & 500\\
\end{bmatrix}
\]
\[
n=\begin{bmatrix}
130\\
20\\
10
\end{bmatrix}
\]

```{r}
p<-matrix(c(200,350,500), nrow=1, ncol=3, byrow=TRUE)
n<-matrix(c(130,20,10), nrow=3, ncol=1, byrow=FALSE)
writeLines("pn:"); p;n;p %*% n; writeLines("\n")
writeLines("np:"); n;p;n %*% p; writeLines("\n")
```