---
title: Linear Algebra  Algorithms, Applications, and Techniques
##  Third Edition
author:  Richard Bronson, Gabriel B. Costa, John T. Saccoman
##  Elsevier Inc.
##  Problem Sets
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

#  Chapter 1 
### Problem Set 1.3

(1) For each of the following pairs of matrices A and B, find the products $(AB)^T$ , 
$A^TB^T$ , and $B^TA^T$ and verify that $(AB)^T=B^TA^T$.

(a) \[
A=\begin{bmatrix}
3& 0\\
4& 1
\end{bmatrix}
\]
\[B=\begin{bmatrix}
-1& \quad 2& 1\\
\quad 3& -1& 0
\end{bmatrix}
\]
```{r}
A<-matrix(c(3,0,4,1), nrow=2, ncol=2, byrow=TRUE)
B<-matrix(c(-1,2,1,3,-1,0), nrow=2, ncol=3, byrow=TRUE)
writeLines("(AB)^T");t(A %*% B); writeLines("\n")
writeLines("A^TB^T non-conformable"); writeLines("\n")
writeLines("B^TA^T"); t(B) %*% t(A); writeLines("\n")
```
(b) \[
A=\begin{bmatrix}
2& 2& 2\\
3& 4& 5
\end{bmatrix}
\]
\[B=\begin{bmatrix}
1& 2\\
3& 4\\
5& 6
\end{bmatrix}
\]
```{r}
A<-matrix(c(2,2,2,3,4,5), nrow=2, ncol=3, byrow=TRUE)
B<-matrix(c(1,2,3,4,5,6), nrow=3, ncol=2, byrow=TRUE)
writeLines("(AB)^T");t(A %*% B); writeLines("\n")
writeLines("A^TB^T"); t(A) %*% t(B); writeLines("\n")
writeLines("B^TA^T"); t(B) %*% t(A); writeLines("\n")
```
(c) \[
A=\begin{bmatrix}
1& 5& -1\\
2& 1& \quad 3\\
0& 7& -8
\end{bmatrix}
\]
\[B=\begin{bmatrix}
\quad 6& \quad 1& \quad 3\\
\quad 2& \quad 0& -1\\
-1& -7 & \quad 2
\end{bmatrix}
\]
```{r}
A<-matrix(c(1,5,-1,2,1,3,0,7,-8), nrow=3, ncol=3, byrow=TRUE)
B<-matrix(c(6,1,3,2,0,-1,-1,-7,2), nrow=3, ncol=3, byrow=TRUE)
writeLines("(AB)^T");t(A %*% B); writeLines("\n")
writeLines("A^TB^T"); t(A) %*% t(B); writeLines("\n")
writeLines("B^TA^T"); t(B) %*% t(A); writeLines("\n")
```
(2) Verify that $(A+B)^T=A^T+B^T$ for the matrices given in part (c) of Problem 1.
```{r}
writeLines("(A+B)^T", sep="\n"); t(A+B)
writeLines("A^T+B^T", sep="\n"); t(A)+t(B)
```
(3) If \[x=\begin{bmatrix}2\\3\\4\end{bmatrix}\] find $x^Tx$ and $xx^T$

```{r}
x<-matrix(c(2,3,4), nrow=3, ncol=1)
x
writeLines("x^Tx"); t(x) %*% x
writeLines("xx^T"); x %*% t(x)
```
\[\begin{bmatrix}a&0\\0&b\end{bmatrix}\begin{bmatrix}c&0\\0&d\end{bmatrix}=\begin{bmatrix}ca&0\\0&bd\end{bmatrix}=
\begin{bmatrix}ac&0\\0&db\end{bmatrix}=\begin{bmatrix}c&0\\0&d\end{bmatrix}\begin{bmatrix}a&0\\0&b\end{bmatrix}\]

(19) Calculate the products AD and BD for
\[
A=\begin{bmatrix}1 & 1 & 1\\1 & 1 & 1\\1 & 1 & 1 \end{bmatrix}
B=\begin{bmatrix}0 &1 & 2\\3 & 4 & 5 \\6 & 7 & 8 \end{bmatrix}
D=\begin{bmatrix}2 &0 & 0\\0 & 3 & 0 \\0 & 0 & -5 \end{bmatrix}
E=\begin{bmatrix}0 &0 & 2\\0 & 3 & 0 \\-5 & 0 & 0 \end{bmatrix}
F=\begin{bmatrix}2 &3 & -5\\0 & 0 & 0 \\0 & 0 & 0 \end{bmatrix}
\]
```{r}
A<-matrix(c(1,1,1,1,1,1,1,1,1), nrow=3, ncol=3, byrow=TRUE)
B<-matrix(c(0,1,2,3,4,5,6,7,8), nrow=3, ncol=3, byrow=TRUE)
D<-matrix(c(2,0,0,0,3,0,0,0,-5), nrow=3, ncol=3, byrow=TRUE)
E<-matrix(c(0,0,2,0,3,0,-5,0,0), nrow=3, ncol=3, byrow=TRUE)
F<-matrix(c(2,3,-5,0,0,0,0,0,0), nrow=3, ncol=3, byrow=TRUE)
A %*% D
B %*% D
D %*% A
D %*% B
A %*% E
B %*% E
A %*% F
B %*% F
```

