---
title: "Linear Algebra  Algorithms, Applications, and Techniques"
author: "Richard Bronson, Gabriel B. Costa, John T. Saccoman"
output:
  html_document:
     toc:  true
     theme: null
     highlight: null
     css: styles.css
---
     
```{r, include=FALSE}
library(dplyr)
library(tidyverse)
```

#  Chapter 3
## Problems 3.2

### (1) 
Define **T** : $\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{ by }
T\begin{bmatrix}
     a&b
\end{bmatrix}=
\begin{bmatrix}
     2a&3b
\end{bmatrix}
\textrm{. Find }\\
(a) T\begin{bmatrix}
     2&3
\end{bmatrix}=
\begin{bmatrix}
     4&9
\end{bmatrix}\\
(b) T\begin{bmatrix}
     -1&5\end{bmatrix}=
\begin{bmatrix}
     -2&15
\end{bmatrix}\\
(c) T\begin{bmatrix}
     -8&200
\end{bmatrix}=
\begin{bmatrix}
     -16&600
\end{bmatrix}\\
(d) T\begin{bmatrix}
     0&-7
\end{bmatrix}=
\begin{bmatrix}
     0&-21
\end{bmatrix}$
     
### (2) 
Define **T** : $\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{ by }T[a b]=[a+2 b-2]$. Find
     (a) T[2 3] = [4 1]
     (b) T[-1 5]= [1 3]
     (c) T[-8 200] = [-6 198]
     (d) T[0 -7] = [2 -9]
     
### (3) 
Define **S** : $\mathbb{R}^3$ $\rightarrow$ $\mathbb{R}^2$ by **S**[a b c]=[a+b c]. Find
     (a) S[1 2 3] = [3 3]
     (b) S[-2 3 -3] = [1 -3]
     (c) S[2 -2 0] = [0 0]
     (d) S[1 4 3] = [5 3]
     
### (4) 
Redo Problem 3 with S[a b c]=[a-c c-b].
     (a) S[1 2 3] = [-2 1]
     (b) S[-2 3 -3] = [1 -6]
     (c) S[2 -2 0] = [2 2]
     (d) S[1 4 3] = [-3 -1]
     
### (5) 
Redo Problem 3 with S[a b c]=[a+2b-3c 0].
     (a) S[1 2 3] = [-4 0]
     (b) S[-2 3 -3] = [13 0]
     (c) S[2 -2 0] = [-2 0]
     (d) S[1 4 3] = [0 0]
     
### (6) 
Define **N** : $\mathbb{R}^2$ $\rightarrow$ $\mathbb{R}^3$ by **N**[a b]=[a+b 2a+b b+2] Find
     N[1 1] = [2 3 3]
     N[2 -3] = [-1 1 -1]
     N[3 0] = [3 6 2]
     N[0 0] = [0 0 2]
     
### (11) 
T[$\alpha$a $\alpha$b] = [2$\alpha$a 3$\alpha$b] = $\alpha$[2a 3b] = $\alpha$T[a b] 
     
### (25) 
S[a b c]=abc;     
     S[$\alpha$(a b c)]=S[$\alpha$a $\alpha$b $\alpha$c] = $\alpha^3$ abc != $\alpha$ abc = $\alpha$S[abc]
     
## Problems 3.3

In Problems 1 through 25, find the matrix representation for T : $\mathbb{V}$ $\rightarrow$ $\mathbb{W}$ with
respect to the given bases, $\mathbb{B}$ for a vector space $\mathbb{V}$ and $\mathbb{C}$ for a vector space $\mathbb{W}$.

### (1) 
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^3 \textrm{ defined by }
T\begin{bmatrix}
     a\\ b\\
\end{bmatrix} =
\begin{bmatrix}
     a+b\\ a-b\\ 2b
\end{bmatrix},
\mathbb{B} =
     \left \{
          \begin{bmatrix}
               1\\0
          \end{bmatrix},
          \begin{bmatrix}
               1\\1
          \end{bmatrix}
     \right \} \textrm{, and }
\mathbb{C} =
     \left \{
          \begin{bmatrix}
               1\\ 0\\ 0
          \end{bmatrix},
          \begin{bmatrix}
               0\\ 1\\ 0
          \end{bmatrix},
          \begin{bmatrix}
               0\\ 0\\ 1
          \end{bmatrix}
     \right \}\\
\begin{aligned}
T\begin{bmatrix} 
     1\\ 0 
\end{bmatrix} &= 
\begin{bmatrix} 
     1+0\\ 1-0\\ 2*0 
\end{bmatrix} = 
\begin{bmatrix} 
     1\\ 1\\ 0 
\end{bmatrix} = 
1\begin{bmatrix}
     1\\ 0\\ 0\\ 
\end{bmatrix} 
+1\begin{bmatrix} 
     0\\ 1\\ 0 
\end{bmatrix} 
+0\begin{bmatrix} 
     0\\ 0\\ 1 
\end{bmatrix} = 
\begin{bmatrix} 
     1\\ 1\\ 0 
\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix} 
     1\\ 1 
\end{bmatrix} &= 
\begin{bmatrix} 
     1+1\\ 1-1\\ 2*1 
\end{bmatrix} = 
\begin{bmatrix} 
     2\\ 0\\ 2 
\end{bmatrix} = 
2\begin{bmatrix}
     1\\ 0\\ 0\\ 
\end{bmatrix} +
0\begin{bmatrix} 
     0\\ 1\\ 0 
\end{bmatrix} + 
2\begin{bmatrix} 
     0\\ 0\\ 1 
\end{bmatrix} = 
\begin{bmatrix} 
     2\\ 1\\ 2 
\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
     \begin{bmatrix} 
          1 & 2\\ 1 & 0\\ 0 & 2 
     \end{bmatrix}_\mathbb{C}
     \end{aligned}$

### (2) 
$\textrm{Problem 1 with }
\mathbb{B} = 
     \left \{ 
          \begin{bmatrix} 
               1\\ 1 
          \end{bmatrix}, 
          \begin{bmatrix} 
               1\\ 2 
          \end{bmatrix}
     \right \}\\
\begin{aligned}
T\begin{bmatrix} 
     1\\ 1 
\end{bmatrix} &= 
\begin{bmatrix} 
     1+1\\ 1-1\\ 2*1 
\end{bmatrix} = 
\begin{bmatrix} 
     2\\ 0\\ 2 
\end{bmatrix}\\
T\begin{bmatrix} 
     1\\ 2 
\end{bmatrix} &= 
\begin{bmatrix} 
     1+2\\ 1-2\\ 2*2 
\end{bmatrix} = 
\begin{bmatrix} 
     3\\ -1\\ 4 
\end{bmatrix}\\
T&\leftrightarrow 
     \begin{bmatrix} 
          2 & 3\\ 0 & -1\\ 2 & 4 
     \end{bmatrix}_\mathbb{C}
\end{aligned}$

### (3) 
$\textrm{Problem 1 with }
\mathbb{C} = 
     \left \{ 
          \begin{bmatrix} 
               1\\ 1\\ 0
          \end{bmatrix}, 
          \begin{bmatrix}
               1\\ 0\\ 1
          \end{bmatrix},
          \begin{bmatrix}
               0\\ 1\\ 0
          \end{bmatrix}
     \right \}\\
\begin{align}
T\begin{bmatrix}
     1\\ 0
\end{bmatrix} &=
\begin{bmatrix} 
     1+0\\ 1-0\\ 2*0
\end{bmatrix} = 
\begin{bmatrix} 
     1\\ 1\\ 0
\end{bmatrix} = 
1\begin{bmatrix}
     1\\ 1\\ 0\\
\end{bmatrix}
+0\begin{bmatrix}
     1\\ 0\\ 1
\end{bmatrix}
+0\begin{bmatrix}
     0\\ 1\\ 0
\end{bmatrix} = 
\begin{bmatrix} 
     1\\ 0\\ 0 
\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix} 
     1\\ 1
\end{bmatrix} &= 
\begin{bmatrix}
     1+1\\ 1-1\\ 2*1
\end{bmatrix} = 
\begin{bmatrix}
     2\\ 0\\ 2
\end{bmatrix} = 
0\begin{bmatrix}
     1\\ 1\\ 0\\
\end{bmatrix}
+2\begin{bmatrix}
     1\\ 0\\ 1
\end{bmatrix}
+0\begin{bmatrix}
     0\\ 1\\ 0
\end{bmatrix} = 
\begin{bmatrix} 
     0\\ 2\\ 0 
\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
\begin{bmatrix} 
     1 & 0\\ 0 & 2\\ 0 & 0 
\end{bmatrix}_\mathbb{C}
\end{align}$

### (4) 
$\textrm{Problem 1 with }
\mathbb{B} =
     \left \{ 
          \begin{bmatrix}
               1\\ 1
          \end{bmatrix},
          \begin{bmatrix}
               1\\ 2
          \end{bmatrix}
     \right \}
\textrm{ and }
\mathbb{C} = 
     \left \{
          \begin{bmatrix}
               1\\ 1\\ 0
          \end{bmatrix},
          \begin{bmatrix}
               1\\ 0\\ 1
          \end{bmatrix},
          \begin{bmatrix}
               0\\ 1\\ 0
          \end{bmatrix}
     \right \}\\
\begin{align}
T\begin{bmatrix}
     1\\ 1 
\end{bmatrix} &= 
     \begin{bmatrix} 
          1+1\\ 1-1\\ 2*1
     \end{bmatrix}= 
     \begin{bmatrix}
          2\\ 0\\ 2
     \end{bmatrix}=
     0\begin{bmatrix}
          1\\ 1\\ 0
     \end{bmatrix}
     +2\begin{bmatrix}
          1\\ 0\\ 1
     \end{bmatrix}
     +0\begin{bmatrix}
          0\\ 1\\ 0
     \end{bmatrix}=
     \begin{bmatrix}
          0\\ 2\\ 0
     \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}
     1\\ 2
\end{bmatrix} &=
     \begin{bmatrix}
          1+2\\ 1-2\\ 2*2
     \end{bmatrix}=
     \begin{bmatrix}
          3\\ -1\\ 4
     \end{bmatrix} =
     -1\begin{bmatrix}
          1\\ 1\\ 0
     \end{bmatrix}
     +4\begin{bmatrix}
          1\\ 0\\ 1
     \end{bmatrix}
     +0\begin{bmatrix}
          0\\ 1\\ 0
     \end{bmatrix} = 
     \begin{bmatrix}
          -1\\ 4\\ 0
     \end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
     \begin{bmatrix}
          0 & -1\\ 2 & 4\\ 0 & 0
     \end{bmatrix}_\mathbb{C}
\end{align}$

### (5)  
$T:\mathbb{R}^3 \rightarrow \mathbb{R}^2 \textrm{ defined by }
T\begin{bmatrix}
     a\\ b\\ c \end{bmatrix} = \begin{bmatrix}2a+3b-c\\ 4b+5c \end{bmatrix} \textrm{, and }
\mathbb{B} = \left \{ \begin{bmatrix}1\\ 0\\ 0 \end{bmatrix}, \begin{bmatrix}1\\ 1\\ 0 \end{bmatrix}, \begin{bmatrix}1\\ 1\\ 1 \end{bmatrix} \right \} \textrm{, and }
\mathbb{C} = \left \{ \begin{bmatrix}1\\1 \end{bmatrix}, \begin{bmatrix}0\\1 \end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}1\\0\\0 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(0)-0\\4(0)+5(0) \end{bmatrix}=\begin{bmatrix}2\\0 \end{bmatrix}=2\begin{bmatrix}1\\1 \end{bmatrix} -2\begin{bmatrix}0\\1 \end{bmatrix}=\begin{bmatrix}2\\-2 \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\1\\0 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(1)-0\\4(1)+5(0) \end{bmatrix}=\begin{bmatrix}5\\4 \end{bmatrix}=5\begin{bmatrix}1\\1 \end{bmatrix} -1\begin{bmatrix}0\\1 \end{bmatrix}=\begin{bmatrix}5\\-1 \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\1\\1 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(1)-1\\4(1)+5(1) \end{bmatrix}=\begin{bmatrix}3\\9 \end{bmatrix}=3\begin{bmatrix}1\\1 \end{bmatrix} +6\begin{bmatrix}0\\1 \end{bmatrix}=\begin{bmatrix}3\\6 \end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow \begin{bmatrix}2&5&3\\-2&-1&6 \end{bmatrix}_\mathbb{C}
\end{align}$
     
### (6)  
$\textrm{Problem 5 with }
\mathbb{B} = \left \{ \begin{bmatrix}1\\ -1\\ 0 \end{bmatrix}, \begin{bmatrix}1\\ 0\\ -1 \end{bmatrix}, \begin{bmatrix}-1\\ 1\\ 1 \end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}1\\-1\\0 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(-1)-0\\4(-1)+5(0) \end{bmatrix}=\begin{bmatrix}-1\\-4 \end{bmatrix}=-1\begin{bmatrix}1\\1 \end{bmatrix} -3\begin{bmatrix}0\\1 \end{bmatrix}=\begin{bmatrix}-1\\-3 \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\0\\-1 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(0)-(-1)\\4(0)+5(-1) \end{bmatrix}=\begin{bmatrix}3\\-5 \end{bmatrix}=3\begin{bmatrix}1\\1 \end{bmatrix} -8\begin{bmatrix}0\\1 \end{bmatrix}=\begin{bmatrix}3\\-8 \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}-1\\1\\1 \end{bmatrix} &= \begin{bmatrix} 2(-1)+3(1)-1\\4(1)+5(1) \end{bmatrix}=\begin{bmatrix}0\\9 \end{bmatrix}=0\begin{bmatrix}1\\1 \end{bmatrix} +9\begin{bmatrix}0\\1 \end{bmatrix}=\begin{bmatrix}0\\9 \end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow \begin{bmatrix}-1&3&0\\-3&-8&9 \end{bmatrix}_\mathbb{C}
\end{align}$

### (7) 
$\textrm{Problem 5 with }
\mathbb{C} = \left \{ \begin{bmatrix}1\\1 \end{bmatrix}, \begin{bmatrix}1\\-1 \end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}1\\0\\0 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(0)-0\\4(0)+5(0) \end{bmatrix}=\begin{bmatrix}2\\0 \end{bmatrix}=1\begin{bmatrix}1\\1 \end{bmatrix} +1\begin{bmatrix}1\\-1 \end{bmatrix}=\begin{bmatrix}1\\-1 \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\1\\0 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(1)-0\\4(1)+5(0) \end{bmatrix}=\begin{bmatrix}5\\4 \end{bmatrix}=4.5\begin{bmatrix}1\\1 \end{bmatrix} +.5\begin{bmatrix}1\\-1 \end{bmatrix}=\begin{bmatrix}4.5\\.5 \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\1\\1 \end{bmatrix} &= \begin{bmatrix} 2(1)+3(1)-1\\4(1)+5(1) \end{bmatrix}=\begin{bmatrix}3\\9 \end{bmatrix}=6\begin{bmatrix}1\\1 \end{bmatrix} -3\begin{bmatrix}1\\-1 \end{bmatrix}=\begin{bmatrix}6\\-3 \end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow \begin{bmatrix}1&4.5&6\\-1&.5&-3 \end{bmatrix}_\mathbb{C}
\end{align}$
     
### (8)  
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^3 \textrm{ defined by}
T\begin{bmatrix} 
     a\\ b\\ 
\end{bmatrix} = 
\begin{bmatrix} 
     a+b\\ a-b\\ 2b 
\end{bmatrix},
\mathbb{B} = 
     \left \{ 
          \begin{bmatrix} 
               1\\1
          \end{bmatrix}, 
          \begin{bmatrix} 
               1\\-1
          \end{bmatrix} 
     \right \} \textrm{, and}
\mathbb{C} = 
     \left \{ 
          \begin{bmatrix} 
               1\\-1\\0 
          \end{bmatrix}, 
          \begin{bmatrix} 
               1\\0\\-1
          \end{bmatrix}, 
          \begin{bmatrix} 
               -1\\1\\1
          \end{bmatrix} 
     \right \}\\
T\begin{bmatrix} 
     1\\1
\end{bmatrix} = 
\begin{bmatrix} 
     1+1\\ 1-1\\ 2*1 
\end{bmatrix} = 
\begin{bmatrix} 
     2\\0\\2 
\end{bmatrix} = 
x\begin{bmatrix}
     1\\-1\\0
\end{bmatrix} 
+y\begin{bmatrix} 
     1\\0\\-1
\end{bmatrix} 
+z\begin{bmatrix} 
     -1\\ 1\\1 
\end{bmatrix}, 
\left ( 
     \begin{array}{lcl} 
          x+y-z&=&2\\-x+z&=&0\\-y+z&=&2 
     \end{array} 
\right ) 
\therefore  
\begin{bmatrix}
     x\\y\\z
\end{bmatrix}=
\begin{bmatrix} 
     4\\2\\4 
\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix} 
     1\\-1 
\end{bmatrix} = 
\begin{bmatrix} 
     1+(-1)\\ 1-(-1)\\ 2*(-1) 
\end{bmatrix} = 
\begin{bmatrix} 
     0\\ 2\\ -2 
\end{bmatrix} = 
x\begin{bmatrix}
     1\\-1\\0\\ 
\end{bmatrix} 
+y\begin{bmatrix} 
     1\\0\\-1
\end{bmatrix} 
+z\begin{bmatrix} 
     -1\\1\\1
\end{bmatrix},\\ 
\left ( 
     \begin{array}{lcl} 
          x+y-z&=&0\\-x+z&=&2\\-y+z&=&-2 
     \end{array} 
\right ) 
\therefore 
\begin{bmatrix}
     x\\y\\z
\end{bmatrix}=
\begin{bmatrix} 
     -2\\2\\0 
\end{bmatrix}_\mathbb{C}\\
T\leftrightarrow \begin{bmatrix} 4 & -2\\ 2 & 2\\ 4 & 0 \end{bmatrix}_\mathbb{C}$

### (9)  
$T:\mathbb{R}^3 \rightarrow \mathbb{R}^2 \textrm{ defined by }
T\begin{bmatrix}a\\ b\\ c \end{bmatrix} = \begin{bmatrix}a+2b-3c\\ 9a-8b-7c \end{bmatrix} \textrm{, and }
\mathbb{B} = 
     \left \{ 
          \begin{bmatrix}1\\ 0\\ 0 \end{bmatrix}, 
          \begin{bmatrix}1\\ 1\\ 0 \end{bmatrix}, 
          \begin{bmatrix}1\\ 1\\ 1 \end{bmatrix} 
     \right \} \textrm{, and }
\mathbb{C} = 
     \left \{ 
          \begin{bmatrix}1\\1 \end{bmatrix}, 
          \begin{bmatrix}0\\1 \end{bmatrix} 
     \right \}\\
\begin{align}
T\begin{bmatrix}1\\0\\0\end{bmatrix} &= 
     \begin{bmatrix} (1)+2(0)-3(0)\\9(1)-8(0)-7(0)\end{bmatrix}=
     \begin{bmatrix}1\\9\end{bmatrix}=
     1\begin{bmatrix}1\\1 \end{bmatrix} +8\begin{bmatrix}0\\1 \end{bmatrix}=
     \begin{bmatrix}1\\8 \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\1\\0 \end{bmatrix} &= 
     \begin{bmatrix} (1)+2(1)-3(0)\\9(1)-8(1)-7(0) \end{bmatrix}=
     \begin{bmatrix}3\\1 \end{bmatrix}=
     3\begin{bmatrix}1\\1 \end{bmatrix}
     -2\begin{bmatrix}0\\1 \end{bmatrix}=
     \begin{bmatrix}3\\-2\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\1\\1 \end{bmatrix} &= 
     \begin{bmatrix} (1)+2(1)-3(1)\\9(1)-8(1)-7(1)\end{bmatrix}=
     \begin{bmatrix}0\\-6\end{bmatrix}=
     0\begin{bmatrix}1\\1 \end{bmatrix}
     -6\begin{bmatrix}0\\1 \end{bmatrix}=
     \begin{bmatrix}0\\-6 \end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow \begin{bmatrix}1&3&0\\8&-2&-6 \end{bmatrix}_\mathbb{C}
\end{align}$
     
### (10) 
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{defined by}
T\begin{bmatrix}a\\b\end{bmatrix} = \begin{bmatrix}25a+30b\\-45a+50b\end{bmatrix}\textrm{, and} 
\mathbb{B}=\mathbb{C}=\left \{ \begin{bmatrix}1\\0\end{bmatrix},\begin{bmatrix}0\\1\end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}1\\0\end{bmatrix}&=
     \begin{bmatrix}25(1)+30(0)\\-45(1)+50(0)\end{bmatrix}=
     \begin{bmatrix}25\\-45\end{bmatrix}=
     25\begin{bmatrix}1\\0\end{bmatrix}
     -45\begin{bmatrix}0\\1\end{bmatrix}=
     \begin{bmatrix}25\\-45\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}0\\1\end{bmatrix}&=
     \begin{bmatrix}25(0)+30(1)\\-45(0)+50(1)\end{bmatrix}=
     \begin{bmatrix}30\\50\end{bmatrix}=
     30\begin{bmatrix}1\\0\end{bmatrix}
     +50\begin{bmatrix}0\\1\end{bmatrix}=
     \begin{bmatrix}30\\50\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
     \begin{bmatrix}
          25&30\\-45&50
     \end{bmatrix}_\mathbb{C}
\end{align}$
     
### (11) 
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{ defined by }
T\begin{bmatrix}a\\b\end{bmatrix} = \begin{bmatrix}25a+30b\\-45a+50b\end{bmatrix}\textrm{, and }
\mathbb{B}=\left \{ \begin{bmatrix}10\\10\end{bmatrix},\begin{bmatrix}0\\5\end{bmatrix} \right \}, 
\mathbb{C}=\left \{ \begin{bmatrix}1\\0\end{bmatrix},\begin{bmatrix}0\\1\end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}10\\10\end{bmatrix}&=
     \begin{bmatrix}25(10)+30(10)\\-45(10)+50(10)\end{bmatrix}=
     \begin{bmatrix}550\\50\end{bmatrix}=
     550\begin{bmatrix}1\\0\end{bmatrix}
     +50\begin{bmatrix}0\\1\end{bmatrix}=
     \begin{bmatrix}550\\50\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}0\\5\end{bmatrix}&=
     \begin{bmatrix}25(0)+30(5)\\-45(0)+50(5)\end{bmatrix}=
     \begin{bmatrix}150\\250\end{bmatrix}=
     150\begin{bmatrix}1\\0\end{bmatrix}
     +250\begin{bmatrix}0\\1\end{bmatrix}=
     \begin{bmatrix}150\\250\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
     \begin{bmatrix}
          550&50\\150&250
     \end{bmatrix}_\mathbb{C}
\end{align}$
          
### (12) 
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{ defined by }
T\begin{bmatrix}a\\b\end{bmatrix} = \begin{bmatrix}25a+30b\\-45a+50b\end{bmatrix} \textrm{, and }
\mathbb{B}=\left \{ \begin{bmatrix}1\\0\end{bmatrix},\begin{bmatrix}0\\1\end{bmatrix} \right \}
\mathbb{C}=\left \{ \begin{bmatrix}10\\10\end{bmatrix},\begin{bmatrix}0\\5\end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}1\\0\end{bmatrix}&=
     \begin{bmatrix}25(1)+30(0)\\-45(1)+50(0)\end{bmatrix}=
     \begin{bmatrix}25\\-45\end{bmatrix}=
     2.5\begin{bmatrix}10\\10\end{bmatrix}
     -14\begin{bmatrix}0\\5\end{bmatrix}=
     \begin{bmatrix}2.5\\-14\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}0\\1\end{bmatrix}&=
     \begin{bmatrix}25(0)+30(1)\\-45(0)+50(1)\end{bmatrix}=
     \begin{bmatrix}30\\50\end{bmatrix}=
     3\begin{bmatrix}10\\10\end{bmatrix}
     +4\begin{bmatrix}0\\5\end{bmatrix}=
     \begin{bmatrix}3\\4\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
     \begin{bmatrix}
          2.5&3\\-14&4
     \end{bmatrix}_\mathbb{C}
\end{align}$
          
### (13) 
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{ defined by }
T\begin{bmatrix}a\\b\end{bmatrix} = \begin{bmatrix}25a+30b\\-45a+50b\end{bmatrix} \textrm{, and }
\mathbb{B}=\mathbb{C}=\left \{ \begin{bmatrix}10\\10\end{bmatrix},\begin{bmatrix}0\\5\end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}10\\10\end{bmatrix}&=
     \begin{bmatrix}25(10)+30(10)\\-45(10)+50(10)\end{bmatrix}=
     \begin{bmatrix}550\\50\end{bmatrix}=
     55\begin{bmatrix}10\\10\end{bmatrix}
     -100\begin{bmatrix}0\\5\end{bmatrix}=
     \begin{bmatrix}55\\-100\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}0\\5\end{bmatrix}&=
     \begin{bmatrix}25(0)+30(5)\\-45(0)+50(5)\end{bmatrix}=
     \begin{bmatrix}150\\250\end{bmatrix}=
     15\begin{bmatrix}10\\10\end{bmatrix}
     +20\begin{bmatrix}0\\5\end{bmatrix}=
     \begin{bmatrix}15\\20\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
     \begin{bmatrix}
          55&15\\-100&20
     \end{bmatrix}_\mathbb{C}
\end{align}$

### (14) 
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{defined by}
T\begin{bmatrix}a\\b\end{bmatrix} = \begin{bmatrix}25a+30b\\-45a+50b\end{bmatrix} \textrm{, and}\\ 
\mathbb{B}=\left \{ \begin{bmatrix}1\\-1\end{bmatrix},\begin{bmatrix}1\\2\end{bmatrix} \right \}\\
\mathbb{C}=\left \{ \begin{bmatrix}1\\2\end{bmatrix},\begin{bmatrix}2\\1\end{bmatrix} \right \}\\
T\begin{bmatrix}1\\-1\end{bmatrix}=
          \begin{bmatrix}25(1)+30(-1)\\-45(1)+50(-1)\end{bmatrix}=
          \begin{bmatrix}-5\\-95\end{bmatrix}=
          \begin{bmatrix}1&2\\2&1\end{bmatrix}
          \begin{bmatrix}x\\y\end{bmatrix},$
          
```{r}
C<-matrix(c(1,2,2,1), nrow=2, ncol=2, byrow=FALSE)
b<-matrix(c(-5,-95), nrow=2, ncol=1, byrow=FALSE)
solve(C,b)
```

<!---          
          $$
          \left ( 
               \begin{array}{lcl} 
                    x+2y&=&-5\\2x+y&=&-95
               \end{array} 
          \right ), \\
         \left (
               \begin{array}{lcl}
                    x&=&-2y-5\\2(-2y-5)+y&=&-95\\-3y&=&-85\\y&=&\frac{85}{3}\\x&=&\frac{-185}{3}
               \end{array}
          \right )$$
-->

$\therefore 
     \begin{bmatrix}
          x\\y
     \end{bmatrix}=
     \begin{bmatrix} 
          \frac{-185}{3}\\\frac{85}{3}
     \end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}1\\2\end{bmatrix}=
     \begin{bmatrix}25(1)+30(2)\\-45(1)+50(2)\end{bmatrix}=
     \begin{bmatrix}85\\55\end{bmatrix}=
     \begin{bmatrix}1&2\\2&1\end{bmatrix}
     \begin{bmatrix}x\\y\end{bmatrix},$
     
```{r}
C<-matrix(c(1,2,2,1), nrow=2, ncol=2, byrow=FALSE)
b<-matrix(c(85,55), nrow=2, ncol=1, byrow=FALSE)
solve(C,b)
```

     
<!---     
          $$
          \left ( 
               \begin{array}{lcl} 
                    x+2y&=&85\\2x+y&=&55
               \end{array} 
          \right ), \\
          \left ( 
               \begin{array}{lcl} 
                    x&=&-2y+85\\-4y+170+y&=&55\\-3y&=&-115
               \end{array} 
          \right )$$
-->
          
$\therefore 
     \begin{bmatrix}
          x\\y
     \end{bmatrix}=
     \begin{bmatrix} 
          \frac{25}{3}\\ \frac{115}{3}
     \end{bmatrix}_\mathbb{C}\\
T\leftrightarrow 
     \begin{bmatrix}
          \frac{-185}{3}& \frac{25}{3} \\ \frac{85}{3} & \frac{115}{3}
     \end{bmatrix}_\mathbb{C}$ 
          
### (15)
$T:\mathbb{R}^2 \rightarrow \mathbb{R}^2 \textrm{defined by}
T\begin{bmatrix}a\\b\end{bmatrix} = \begin{bmatrix}2a\\3b-a\end{bmatrix}\textrm{, and} 
\mathbb{B}=\mathbb{C}=\left \{ \begin{bmatrix}1\\0\end{bmatrix},\begin{bmatrix}0\\1\end{bmatrix} \right \}\\
\begin{align}
T\begin{bmatrix}1\\0\end{bmatrix}&=
     \begin{bmatrix}2(1)\\3(0)-(1)\end{bmatrix}=
     \begin{bmatrix}2\\-1\end{bmatrix}=
     2\begin{bmatrix}1\\0\end{bmatrix}
     -1\begin{bmatrix}0\\1\end{bmatrix}=
     \begin{bmatrix}2\\-1\end{bmatrix}_\mathbb{C}\\
T\begin{bmatrix}0\\1\end{bmatrix}&=
     \begin{bmatrix}2(0)\\3(1)-(0)\end{bmatrix}=
     \begin{bmatrix}0\\3\end{bmatrix}=
     0\begin{bmatrix}1\\0\end{bmatrix}
     +3\begin{bmatrix}0\\1\end{bmatrix}=
     \begin{bmatrix}0\\3\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow 
     \begin{bmatrix}
          2&0\\-1&3
     \end{bmatrix}_\mathbb{C}
\end{align}$
          
### (16)
skipped

### (17)
$T:\mathbb{P}^2 \rightarrow \mathbb{P}^3 \textrm{ defined by }
T(at^2+bt+c)=t(at^2+bt+c), 
\mathbb{B}=\left \{t^2,t,1 \right \}, 
\mathbb{C}=\left \{t^3,t^2,t,1 \right \}\\
\begin{align}
T(t^2)&=t(t^2)=t^3=1(t^3)+0(t^2)+0(t)+0(1)=\begin{bmatrix}1\\0\\0\\0\end{bmatrix}_\mathbb{C}\\
T(t)&=t(t)=t^2=0(t^3)+1(t^2)+0(t)+0(1)=\begin{bmatrix}0\\1\\0\\0\end{bmatrix}_\mathbb{C}\\
T(1)&=t(1)=t=0(t^3)+0(t^2)+1(t)+0(1)=\begin{bmatrix}0\\0\\1\\0\end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow
     \begin{bmatrix}
          1&0&0\\0&1&0\\0&0&1\\0&0&0 
     \end{bmatrix}_\mathbb{C}
\end{align}$
          
### (18)
$\textrm{Problem 17 with }
\mathbb{B}= \left \{t^2+t, t^2+1, t+1 \right \} \textrm{ and with } 
\mathbb{C}= \left \{t^3, t^2+1, t^2-1, t \right \}\\
\begin{align}
T(t^2+t)&=t(t^2+t)=t^3+t^2=1(t^3)+ \frac{1}{2} (t^2+1)+ \frac{1}{2} (t^2-1) + 0(t) = 
     \begin{bmatrix}1\\ \frac{1}{2} \\ \frac{1}{2} \\0 \end{bmatrix}_\mathbb{C}\\
T(t^2+1)&=t(t^2+1)=t^3+t=1(t^3) + 0(t^2+1) = 0(t^2-1) + 1(t) =
     \begin{bmatrix}1\\0\\0\\1 \end{bmatrix}_\mathbb{C}\\
T(t+1)&=t(t+1)=t^2+t=0(t^3) + \frac{1}{2}(t^2+1)+ \frac{1}{2}(t^2-1) +1(t) =
     \begin{bmatrix} 0\\ \frac{1}{2} \\ \frac{1}{2} \\ 1 \end{bmatrix}_\mathbb{C}\\
T&\leftrightarrow
     \begin{bmatrix}
          1&1&0\\ 
          \frac{1}{2} & 0 & \frac{1}{2}\\ 
          \frac{1}{2} & 0 & \frac{1}{2} \\ 
          0&1&1 
     \end{bmatrix}_\mathbb{C}
\end{align}$
          
### (19)
$T:\mathbb{P}^3 \rightarrow \mathbb{P}^2 \textrm{ defined by } T(at^3+bt^2+ct+d)=3at^2+2bt+c\\
     \mathbb{B}= \left \{ t^3, t^2+1, t^2-1, t \right \} \textrm{ and }\\
     \mathbb{C}= \left \{ t^2+t, t^2+1, t+1 \right \}\\
     T(t^3)=3t^2\\$

```{r}
C<-matrix(c(1,1,0,1,0,1,0,1,1), nrow=3, ncol=3, byrow=FALSE)
b<-matrix(c(3,0,0), nrow=3, ncol=1, byrow=FALSE)
solve(C,b)
```
     
<!---     
     $$
     \left (
          \begin{array}{lcl}
               x+y&=&3\\x+z&=&0\\y+z&=&0
          \end{array}
     \right ), 
     \left (
          \begin{array}{lcl}
               x&=&-z\\y&=&-z\\x&=&y\\2x&=&3\\x&=& \frac{3}{2} \\z&=& \frac{-3}{2}
          \end{array}
     \right ) \\
     $$
-->     

$T(t^3) \rightarrow 
     \begin{bmatrix} 
          \frac{3}{2}\\ \frac{3}{2}\\ \frac{-3}{2} 
     \end{bmatrix}_\mathbb{C}\\
T(t^2+1)=2t, \\$

```{r}
C<-matrix(c(1,1,0,1,0,1,0,1,1), nrow=3, ncol=3, byrow=FALSE)
b<-matrix(c(0,2,0), nrow=3, ncol=1, byrow=FALSE)
solve(C,b)
```

<!---
     $$
     \left (
          \begin{array}{lcl}
               x+y&=&0\\x+z&=&2\\y+z&=&0
          \end{array}
     \right ),
     \left (
          \begin{array}{lcl}
               x&=&-y\\z&=&-y\\x&=&z\\2x&=&2\\x&=&1\\y&=&-1\\z&=&1
          \end{array}
     \right ) \\
     $$
-->
     
$T(t^2+1) \rightarrow 
     \begin{bmatrix}
          1\\-1\\1
     \end{bmatrix}_\mathbb{C}\\
T(t^2-1)=2t \textrm{ (as above) } \\
T(t^2-1) \rightarrow 
     \begin{bmatrix}
          1\\-1\\1
     \end{bmatrix}_\mathbb{C} \\
T(t)=1, \\$

```{r}
C<-matrix(c(1,1,0,1,0,1,0,1,1), nrow=3, ncol=3, byrow=FALSE)
b<-matrix(c(0,0,1), nrow=3, ncol=1, byrow=FALSE)
solve(C,b)
```

<!---
     $$
     \left (
          \begin{array}{lcl}
               x+y&=&0\\x+z&=&0\\y+z&=&1
          \end{array}
     \right ), 
     \left (
          \begin{array}{lcl}
               x&=&-y\\x&=&-z\\y&=&z\\2y&=&1\\y&=& \frac{1}{2} \\ z&=& \frac{1}{2} \\ x&=& \frac{-1}{2}
          \end{array}
     \right )\\
     $$
-->
     
$T(t) \rightarrow
     \begin{bmatrix} 
          \frac{-1}{2} \\ \frac{1}{2} \\ \frac{1}{2} 
     \end{bmatrix}_\mathbb{C}\\
T \leftrightarrow
     \begin{bmatrix}
          \frac{3}{2} & 1 & 1 & \frac{-1}{2} \\
          \frac{3}{2} & -1 & -1 & \frac{1}{2} \\
          \frac{-3}{2} & 1 & 1 & \frac{1}{2}
     \end{bmatrix}_\mathbb{C}$
          
### (20)
$T:\mathbb{P}^2 \rightarrow \mathbb{R}^2 \textrm{ defined by } T(at^2+bt+c)=\begin{bmatrix}2a+b\\3a-4b+c\end{bmatrix}\\
\mathbb{B}=\left \{ t^2, t^2-1, t \right \} \textrm{, and } 
\mathbb{C}=\left \{ \begin{bmatrix}1\\1\end{bmatrix}, \begin{bmatrix}1\\-1\end{bmatrix} \right \}\\
T(t^2)=T(1(t^2)+0(t)+0)=
     \begin{bmatrix}2(1)+0\\3(1)-4(0)+0\end{bmatrix}=
     \begin{bmatrix}2\\3\end{bmatrix}\\$

```{r}
C<-matrix(c(1,1,1,-1), nrow=2, ncol=2, byrow=FALSE)
b<-matrix(c(2,3), nrow=2, ncol=1, byrow=FALSE)
solve(C,b)
```
     
<!---     
     $$
     \left (
          \begin{array}{lcl}
               x+y&=&2\\x-y&=&3
          \end{array}
     \right ), 
     \left (
          \begin{array}{lcl}
               x&=&y+3\\(y+3)+y&=&2\\2y+3&=&2\\y&=& \frac{-1}{2}\\x&=&\frac{5}{2}
          \end{array}
     \right ) \\
     $$
-->     
     
$T(t^2) \rightarrow \begin{bmatrix} \frac{5}{2}\\ \frac{-1}{2} \end{bmatrix}_\mathbb{C}\\
T(t^2-1)=T(1(t^2)+0(t)-1(1))=
\begin{bmatrix} 2(1)+0\\3(1)-4(0)+(-1)\end{bmatrix}=
\begin{bmatrix}2\\2\end{bmatrix}\\$

```{r}
C<-matrix(c(1,1,1,-1), nrow=2, ncol=2, byrow=FALSE)
b<-matrix(c(2,2), nrow=2, ncol=1, byrow=FALSE)
solve(C,b)
```

<!---
     $$
     \left (
          \begin{array}{lcl}
               x+y&=&2\\x-y&=&2
          \end{array}
     \right ), 
     \left (
          \begin{array}{lcl}
               x&=&y+2\\(y+2)+y&=&2\\2y+2&=&2\\y&=&0\\x&=&2
          \end{array}
     \right ) \\     
     $$
-->     
     
$T(t^2-1) \rightarrow \begin{bmatrix}2\\0\end{bmatrix}_\mathbb{C} \\
T(t)=T(0(t^2)+1(t)+0)=
\begin{bmatrix}2(0)+1\\3(0)-4(1)+0\end{bmatrix}=
\begin{bmatrix}1\\-4\end{bmatrix}\\$

```{r}
C<-matrix(c(1,1,1,-1), nrow=2, ncol=2, byrow=FALSE)
b<-matrix(c(1,-4), nrow=2, ncol=1, byrow=FALSE)
solve(C,b)
```

<!---
$$
     \left (
          \begin{array}{lcl}
               x+y&=&1\\x-y&=&-4
          \end{array}
     \right ), 
     \left (
          \begin{array}{lcl}
               x&=&y-4\\(y-4)+y&=&1\\2y-4&=&1\\y&=& \frac{5}{2} \\x&=& \frac{-3}{2}
          \end{array}
     \right ) \\     
     $$
-->
     
$T(t) \rightarrow \begin{bmatrix} \frac{-3}{2} \\ \frac{5}{2} \end{bmatrix}_\mathbb{C} \\
T \leftrightarrow \begin{bmatrix} \frac{5}{2}&2& \frac{-3}{2} \\ \frac{-1}{2}&0& \frac{5}{2} \end{bmatrix}_\mathbb{C}$

### (21)
T: $\mathbb{P}^2 \rightarrow \mathbb{R}^3 \textrm{ defined by } T(at^2+bt+c)=\begin{bmatrix}2a+3b\\4a-5c\\6b+7c\end{bmatrix}\\
     \mathbb{B}=\left \{ t^2, t^2-1, t \right \} \textrm{, and } 
     \mathbb{C}=
          \left \{ 
               \begin{bmatrix}
                    1\\0\\0
               \end{bmatrix}, 
               \begin{bmatrix}
                    1\\1\\0
               \end{bmatrix},
               \begin{bmatrix}
                    1\\1\\1
               \end{bmatrix}
          \right \}\\
     T(t^2)=T(1(t^2)+0(t)+0)=
          \begin{bmatrix}
               2(1)+3(0)\\4(1)-5(0)\\6(0)+7(0)
          \end{bmatrix}=
          \begin{bmatrix}
               2\\4\\0
          \end{bmatrix}=
          \begin{bmatrix}
               1&1&1\\0&1&1\\0&0&1
          \end{bmatrix}
          \begin{bmatrix}
               x\\y\\z
          \end{bmatrix}$

```{r}
C<-matrix(c(1,1,1,0,1,1,0,0,1), nrow=3, ncol=3, byrow=TRUE)
b<-matrix(c(2,4,0), nrow=3, ncol=1, byrow=FALSE)
solve(C,b)
```

<!---
          $$
          \left (
               \begin{array}{lcl}
                    x+y+z&=&2\\y+z&=&4\\z&=&0
               \end{array}
          \right ), 
          \left (
               \begin{array}{lcl}
                    y+0&=&4\\y&=&4\\x+4+0&=&2\\x&=& -2
               \end{array}
          \right ) \\ 
          $$
-->

$T(t^2)\rightarrow 
     \begin{bmatrix}
          -2\\4\\0
     \end{bmatrix}\\
T(t^2-1)=T(1(t^2)+0(t)-1(1))=
     \begin{bmatrix}
          2(1)+3(0)\\4(1)-5(-1)\\6(0)+7(-1)
     \end{bmatrix}=
     \begin{bmatrix}
          2\\9\\-7
     \end{bmatrix}=
     \begin{bmatrix}1&1&1\\0&1&1\\0&0&1\end{bmatrix}
     \begin{bmatrix}x\\y\\z\end{bmatrix}$
     
```{r}
C<-matrix(c(1,1,1,0,1,1,0,0,1), nrow=3, ncol=3, byrow=TRUE)
b<-matrix(c(2,9,-7), nrow=3, ncol=1, byrow=FALSE)
solve(C,b)
```
     
<!---     
          $$
          \left (
               \begin{array}{lcl}
                    x+y+z&=&2\\y+z&=&9\\z&=&-7
               \end{array}
          \right ), 
          \left (
               \begin{array}{lcl}
                    y-7&=&9\\y&=&16\\x+16-7&=&2\\x&=& -7
               \end{array}
          \right ) \\ 
          $$
-->
          
$T(t^2-1)\rightarrow
     \begin{bmatrix}
          -7\\16\\-7
     \end{bmatrix}_\mathbb{C}\\
T(t)=T(0(t^2)+1(t)+0)=
     \begin{bmatrix}
          2(0)+3(1)\\4(0)-5(0)\\6(1)+7(0)
     \end{bmatrix}=
     \begin{bmatrix}
          3\\0\\6
     \end{bmatrix}=
     \begin{bmatrix}1&1&1\\0&1&1\\0&0&1\end{bmatrix}
     \begin{bmatrix}x\\y\\z\end{bmatrix}\\$
          
```{r}
C<-matrix(c(1,1,1,0,1,1,0,0,1), nrow=3, ncol=3, byrow=TRUE)
b<-matrix(c(3,0,6), nrow=3, ncol=1, byrow=FALSE)
solve(C,b)
```
          
<!---          
          $$
           \left (
               \begin{array}{lcl}
                    x+y+z&=&3\\y+z&=&0\\z&=&6
               \end{array}
          \right ), 
          \left (
               \begin{array}{lcl}
                    y+6&=&0\\y&=&-6\\x-6+6&=&3\\x&=&3
               \end{array}
          \right ) \\          
          $$
-->
          
$T(t)\rightarrow \begin{bmatrix}3\\-6\\6\end{bmatrix}_\mathbb{C}\\
T\leftrightarrow
     \begin{bmatrix}
          -2&-7&3\\
          4&16&-6\\
          0&-7&6
     \end{bmatrix}_\mathbb{C}$
     
### (22)
$T:\mathbb{P}^2\rightarrow\mathbb{M}_{2X2}\textrm{ defined by } 
T(at^2+bt+c)=\begin{bmatrix}2a+b&c-3a\\4a-5c&6b+7c\end{bmatrix},\\
\mathbb{B}=\left \{ t^2, t^2-1, t \right \}\textrm{, and }\\
\mathbb{C}=\left \{ 
     \begin{bmatrix}1&0\\0&0\end{bmatrix}, 
     \begin{bmatrix}1&1\\0&0\end{bmatrix}, 
     \begin{bmatrix}0&0\\1&1\end{bmatrix}, 
     \begin{bmatrix}0&0\\1&-1\end{bmatrix} 
     \right \}\\
T(t^2)=T(1(t^2)+0(t)+0)=
     \begin{bmatrix}
          2(1)+0&0-3(1)\\4(1)-5(0)&6(0)+7(0)
     \end{bmatrix}=
     \begin{bmatrix}
          2&-3\\4&0
     \end{bmatrix}\\
     \begin{bmatrix}
          2&-3\\4&0
     \end{bmatrix}=
     x\begin{bmatrix}1&0\\0&0\end{bmatrix}+
     y\begin{bmatrix}1&1\\0&0\end{bmatrix}+
     z\begin{bmatrix}0&0\\1&1\end{bmatrix}+
     w\begin{bmatrix}0&0\\1&-1\end{bmatrix}\\$
$$
\left (
     \begin{array}{lcl}
          x+y&=&2\\y&=&-3\\z+w&=&4\\z-w&=& 0
     \end{array}
\right ), 
\left (
     \begin{array}{lcl}
          y&=&-3\\x&=&5\\z&=&2\\w&=&2
     \end{array}
\right ) \\ 
$$
$T(t^2)\rightarrow\begin{bmatrix}5\\-3\\2\\2\end{bmatrix}\\
T(t^2-1)=T((1)t^2+(0)t+(-1)1)=
     \begin{bmatrix}
          2(1)+0&(-1)-3(1)\\
          4(1)-5(-1)&6(0)+7(-1)
     \end{bmatrix}=
     \begin{bmatrix}
          2&-4\\
          9&-7
     \end{bmatrix}\\
     \begin{bmatrix}
          2&-4\\
          9&-7
     \end{bmatrix}=     
     x\begin{bmatrix}1&0\\0&0\end{bmatrix}+
     y\begin{bmatrix}1&1\\0&0\end{bmatrix}+
     z\begin{bmatrix}0&0\\1&1\end{bmatrix}+
     w\begin{bmatrix}0&0\\1&-1\end{bmatrix}\\$
$$
\left (
     \begin{array}{lcl}
          x+y&=&2\\y&=&-4\\z+w&=&9\\z-w&=&-7
     \end{array}
\right ), 
\left (
     \begin{array}{lcl}
          y&=&-4\\x&=&6\\z&=&1\\w&=&8
     \end{array}
\right ) \\ 
$$
$T(t^2)\rightarrow\begin{bmatrix}6\\-4\\1\\8\end{bmatrix}\\
T(t)=T((0)t^2+(1)t+(0)1)
     \begin{bmatrix}
          2(0)+1&(0)-3(0)\\
          4(0)-5(0)&6(1)+7(0)
     \end{bmatrix}=
     \begin{bmatrix}
          1&0\\
          0&6
     \end{bmatrix}\\
     \begin{bmatrix}
          1&0\\
          0&6
     \end{bmatrix}=     
     x\begin{bmatrix}1&0\\0&0\end{bmatrix}+
     y\begin{bmatrix}1&1\\0&0\end{bmatrix}+
     z\begin{bmatrix}0&0\\1&1\end{bmatrix}+
     w\begin{bmatrix}0&0\\1&-1\end{bmatrix}\\$
$$
\left (
     \begin{array}{lcl}
          x+y&=&1\\y&=&0\\z+w&=&0\\z-w&=&6
     \end{array}
\right ), 
\left (
     \begin{array}{lcl}
          y&=&0\\x&=&1\\z&=&3\\w&=&-3
     \end{array}
\right ) \\ 
$$
$T(t)\rightarrow\begin{bmatrix}1\\0\\3\\-3\end{bmatrix}\\
T\leftrightarrow\begin{bmatrix}
     5&6&1\\
     -3&-4&0\\
     2&1&3\\
     2&8&-3
     \end{bmatrix}_\mathbb{C}$

```{r}
C<-matrix(c(1,0,0,0,1,1,0,0,0,0,1,1,0,0,1,-1), nrow=4, ncol=4, byrow=FALSE)
b<-matrix(c(2,-3,4,0), nrow=4, ncol=1, byrow=TRUE)
solve(C,b)
```

