---
title: Linear Algebra  Algorithms, Applications, and Techniques Third Edition
author:  Richard Bronson, Gabriel B. Costa, John T. Saccoman Elsevier Inc.
output: 
    html_document:
        theme: null
        highlight: null
        css: styles.css
---

```{r, include=FALSE}
library(dplyr)
library(tidyverse)
```


#  Chapter 1


(1) Determine the orders of the following matrices:

\[
A=\begin{bmatrix}
1 & 2 \\
3 & 4
\end{bmatrix}
\]

\[
B=\begin{bmatrix}
5 & 6 \\
7 & 8
\end{bmatrix}
\]

\[
C=\begin{bmatrix}
-1 & \quad 0 \\
\quad 3 & -3
\end{bmatrix}
\]
```{r}
A<-matrix(c(1,3,2,4), nrow=2, ncol=2, byrow=FALSE)
B<-matrix(c(5,7,6,8), nrow=2, ncol=2, byrow=FALSE)
C<-matrix(c(-1,3,0,-3), nrow=2, ncol=2, byrow=FALSE)
D<-matrix(c(3,-1,3,2,1,2,-2,6), nrow=4, ncol=2, byrow=FALSE)
E<-matrix(c(-2,0,5,5,2,-2,-3,1), nrow=4, ncol=2, byrow=FALSE)
F<-matrix(c(0,-1,0,2,1,0,0,2), nrow=4, ncol=2, byrow=FALSE)
G<-matrix(c(1/2,2/3,1/3,3/5,1/4,-5/6), nrow=2, ncol=3, byrow=FALSE)
H<-matrix(c(sqrt(2), sqrt(2),sqrt(5), sqrt(3), sqrt(5), sqrt(2), sqrt(5), sqrt(2), sqrt(3)), nrow=3, ncol=3, byrow=FALSE)
J<-matrix(c(0,0,0,0,0), nrow=1, ncol=5, byrow=FALSE)
```

(2) Find, if they exist, the elements in the 1-2 and 3-1 positions for each of the matrices defined in Problem 1.
```{r, warning=FALSE, message=FALSE, error=FALSE}
A[1,2]; 'A[3,1] Does Not Exist'
B[1,2]
C[1,2];
D[1,2]; D[3,1]
E[1,2]; E[3,1]
F[1,2]; F[3,1]
G[1,2]
H[1,2]; H[3,1]
J[1,2]
```
(3) Find, if they exist, a~11~ , a~21~ , b~32~ , d~32~ , d~23~ , e~22~ , g~23~ , h~33~ , and j~21~ for the matrices defined in Problem 1.
```{r, warning=FALSE, message=FALSE, error=FALSE}
cat("A[1,1]", sep="=", A[1,1]);
A[2,1]
'B[3,2] Does Not Exist'
cat("D[3,2]", sep="=", D[3,2])
'D[2,3] Does Not Exist'
E[2,2]
G[2,3]
H[3,3]
'J[2,1] Does not Exit'
```
(4) Determine which, if any, of the matrices defined in Problem 1 are square.
```{r}
"A";if(dim(A)[1]==dim(A)[2]) 1
"B";if(dim(B)[1]==dim(B)[2]) 1
"C";if(dim(C)[1]==dim(C)[2]) 1
"D";if(dim(D)[1]==dim(D)[2]) 1
"E";if(dim(E)[1]==dim(E)[2]) 1
"F";if(dim(F)[1]==dim(F)[2]) 1
"G";if(dim(G)[1]==dim(G)[2]) 1
"H";if(dim(H)[1]==dim(H)[2]) 1
"J";if(dim(J)[1]==dim(J)[2]) 1
```

(5) Determine which, if any, of the matrices defined in Problem 1 are row matrices and which are column matrices.
     
(6) Construct a 4-dimensional column matrix having the value j as its jth component.
```{r, eval=TRUE}
L<-matrix(1:4, nrow=4, ncol=1)
L
```
     
(7) Construct a 5-dimensional row matrix having the value i^2^ as its ith component.
```{r}
M<-matrix((1:5)^2, nrow=1)
M
```
(8) Construct the 2 x 2 matrix A having a~ij~=(-1)^(i+j)^.
```{r}
i<-1:2
j<-1:2
cust_fun<-function(x,y){
     z<-(-1)^(x+y)
     return(z)
}
outer(i,j,cust_fun)
```
(9) Construct the 3 x 3 matrix A having a~ij~ = i/j.
```{r}
i<-1:3
j<-1:3
outer(i,j,"/")
```     
(10) Construct the n x n matrix B having b~ij~ = n - i - j. What will this matrix be when specialized to the 3 x 3 case?
```{r}
n<-3
i<-1:n
j<-1:n
cust_fun<-function(x,y){
     z<-n-x-y
     return(z)
}
outer(i,j,cust_fun)
```
(11) Construct the 2 x 4 matrix C having 
\[
c_{ij} =  \begin{cases}
     i&   \text{if i=1},\\
     j&   \text{if i=2}.
     \end{cases}
\]
```{r}
i<-1:2
j<-1:4
cust_fun<-function(x,y){
     z<-case_when(
          x==1 ~ x,
          x==2 ~ y
     )
     return(z)
}
outer(i,j,cust_fun)
```
(12) Construct the 3 x 4 matrix D having
\[
d_{ij} =  \begin{cases}
     i+j & \text{if i>j }\\
     0 &   \text{if i=j}\\ 
     i-j & \text{if i<j} 
\end{cases}
\]
```{r}
i<-1:3
j<-1:4
cust_fun<-function(x,y){
     z<-case_when(
          x>y ~ x+y,
          x==y ~ x-x,
          x<y ~ x-y
     )
     return(z)
}
outer(i,j,cust_fun)
```
In Problems 13 through 30, perform the indicated operations on the matrices defined in Problem 1.

(13) 2A. 
```{r}
2*A
```
(14) -5A. 
```{r}
-5*A
```
(15) 3D. 
```{r}
3*D
```
(16) 10E.
```{r}
10*E
```
(17) -F. 
```{r}
-1*F
```
(18) A + B. 
```{r}
A+B
```
(19) C + A.
```{r}
C+A
```
(20) D + E.
```{r}
D+E
```
(21) D + F. 
```{r}
D+F
```
(22) A + D. 
Non-conformable arrays
(23) A - B. 
```{r}
A-B
```
(24) C - A.
```{r}
C-A
```
(25) D - E. 
```{r}
D-E
```
(26) D - F. 
```{r}
D-F
```
(27) 2A + 3B. 
```{r}
2*A+3*B
```
(28) 3A - 2C.
```{r}
3*A-2*C
```
(29) 0.1A + 0.2C. 
```{r}
0.1*A+0.2*C
```
(30) -2E + F.
```{r}
-2*E+F
```

The matrices A through F in Problems 31 through 36 are defined in Problem 1.

(31) Find X if A + X = B.


(32) Find Y if 2B + Y = C.

(33) Find X if 3D - X = E.

(34) Find Y if E - 2Y = F.

(35) Find R if 4A + 5R = 10C.

(36) Find S if 3 F - 2S = D.

(42) Store 1 of a three-store chain has 3 refrigerators, 5 stoves, 3 washing machines, and 4 dryers in stock. Store 2 has in stock no refrigerators, 2 stoves, 9 washing machines, and 5 dryers; while store 3 has in stock 4 refrigerators, 2 stoves, and no washing machines or dryers. Present the inventory of the entire chain as a matrix.
```{r}
S<-matrix(c(3,5,3,4,3,2,9,5,4,2,0,0),nrow=3, byrow=TRUE)
S
```
(43) The number of damaged items delivered by the SleepTight Mattress Company from its various plants during the past year is given by the damage matrix
```{r}
K<-matrix(c(80,50,90,12,40,10,16,16,50), nrow=3, ncol=3, byrow=FALSE)
rownames(K)<-c("Michigan","Texas","Utah")
colnames(K)<-c("regular","firm","extra-firm")
K
```
The rows pertain to its three plants in Michigan, Texas, and Utah; the columns pertain to its regular model, its firm model, and its extra-firm model, respectively. The company’s goal for next year is to reduce by 10% the number of damaged regular mattresses shipped by each plant, to reduce by 20% the number of damaged firm mattresses shipped by its Texas plant, to reduce by 30% the number of damaged extra-firm mattresses shipped by its Utah plant, and to keep all other entries the same as last year. What will next year’s damage matrix be if all goals are realized?
```{r}
A<-matrix(c(8,5,9,0,8,0,0,0,15), nrow=3, byrow=FALSE)
K-A
```
 
(44) On January 1, Ms. Smith buys three certificates of deposit from different institutions, all maturing in one year. The first is for $1000 at 7%, the second is for $2000 at 7.5%, and the third is for $3000 at 7.25%. All interest rates are effective on an annual basis. Represent in a matrix all the relevant information regarding Ms. Smith’s investments.

(45) (a) Mr. Jones owns 200 shares of IBM and 150 shares of AT&T. Construct a 1  2 portfolio matrix that reflects Mr. Jones’ holdings.

(b) Over the next year, Mr. Jones triples his holdings in each company. What is his new portfolio matrix?

(c) The following year, Mr. Jones sells shares of each company in his portfolio. The number of shares sold is given by the matrix [50 100], where the first component refers to shares of IBM stock. What is his new portfolio matrix?

(46) The inventory of an appliance store can be given by a 1  4 matrix in which the first entry represents the number of television sets, the second entry the number of air conditioners, the third entry the number of refrigerators, and the fourth entry the number of dishwashers.
     (a) Determine the inventory given on January 1 by [15 2 8 6].

     (b) January sales are given by [4 0 2 3]. What is the inventory matrix on February 1?

     (c) February sales are given by [5 0 3 3], and new stock added in February is given by [3 2 7 8]. What is the inventory matrix on March 1?

(47) The daily gasoline supply of a local service station is given by a 1  3 matrix in which the first entry represents gallons of regular, the second entry gallons of premium, and the third entry gallons of super.
     (a) Determine the supply of gasoline at the close of business on Monday given by [14,000 8000 6000].

     (b) Tuesday’s sales are given by [3500 2000 1500]. What is the inventory matrix at day’s end?
     (c) Wednesday’s sales are given by [5000 1500 1200]. In addition, the station received a delivery of 30,000 gallons of regular, 10,000 gallons of premium, but no super. What is the inventory at day’s end?